---
title: "README"
author: "Dariya Sydykova"
date: "6/19/2019"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Directory structure
The following tree demonstrates the files that are contained in this repository. This section is meant to give you an overview of the information contained here. The following section will explain in detail the content of each folder.
```{r echo=FALSE}
library(fs)
dir_tree(path = ".", recurse = 1)
```

This repo is broken down into two main sub-directories,`evolving_q_sim` and `fixed_q_sim`. The sub-directory `evolving_q_sim` contains code to simulate populations that can evolve epistasic interactions among different genotypes (denoted as `q` throughout), and the sub-directory `fixed_q_sim` contains code to simulate populations that cannot evolve epistatic interactions. The latter maintains the same `q` throughout the time of a simulation. 

Each of these sub-directories contains a folder `src` that contains code to run simulations and to analyze simulation results. A folder `plots` contains figures made for the paper.